Augraphy: A Data Augmentation Library for Document Images

### 2023-02-11 paper.tex
have paper title match easychair title

\title{Augraphy: An Augmentation Pipeline API for Modern Document Images}
%\author{Alexander Groleau\inst{1,2} \and
%Kok Wei Chee\inst{1} \and
%Samay Maini\inst{1} \and
%Jonathan Boarman\inst{1}}
%
%\authorrunning{A. Groleau et al.}
%
%\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
%\and
%Left Associates LLC (\email{research@left.associates})}

@@

    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the noise seen in (a), which is a real-life sample from  RVL-CDIP. We re-created a clean version of (a) in (b). We then create a noisy version of (b) by applying several augmentations to it to produce (c).}

@@

A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers. These are cut to size and stacked, then bound in reams and sent out for sale and use. This is the last time the sheet is clean in its useful lifetime, and even at this point, manufacturing defects can lead to variations in the paper, even between two pages in the same ream. At the point of use, these pages are loaded into a printer where they are stamped or dusted in toner and burned with lasers or sprayed with ink. Any of these processes may alter the local texture or global topology of the sheet. The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to any of a million other operations. Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.

\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle. Every feature just listed already has a direct implementation either within the library or on the development roadmap, with many more planned.

Some techniques exist for introducing these features into images of documents, including but not limited to the following:
\begin{enumerate}
\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used.
\item Similarly, any markup features may be generated and overlaid by the same methods.
\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator's 3D mesh support here is excellent and has inspired \emph{Augraphy} to add similar functionality in its roadmap.  In the meantime, \emph{Augraphy} currently offers support for paper folds.
\end{enumerate}

@@

There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality.

We now discuss each of these:

@@

\section{Deep Learning with \emph{Augraphy}}
\emph{Augraphy} aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks.
This section describes a brief experiment in which \emph{Augraphy} was used to augment a new collection of clean documents, producing a new corpus which fills a feature gap in existing public datasets. This corpus is used to train two denoising convolutional neural networks with different model designs, each of which makes high-accuracy predictions, demonstrating \emph{Augraphy}'s utility for robust data augmentation.

@@

\subsection{Model Architecture}
To evaluate \emph{Augraphy}, we trained two simple models: the first was a UNet convolutional neural network, taken directly from a submission to the NoisyOffice Kaggle competition  \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}. We selected this one for its simplicity and the clarity of its exposition, and use it with few changes. The second model is an off-the-shelf Nonlinear Activation-Free Network (NAFNet), \cite{ref_nafnet}; we again made only minor changes to the model's training hyperparameters, changing the batch size and learning epoch count to fit our training data.

\subsection{Data Generation}
Despite recent techniques (\cite{ref_tvt2040}, \cite{ref_vtssds}) for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its capacity for generalization to new data.

@@

Another new dataset --- \emph{ShabbyReal} --- was produced as part of the larger \emph{ShabbyPages} corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.  \emph{ShabbyReal} is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.

\subsection{Training Regime}
Training of the UNet model proceeded for 600 epochs, learning features from 1050 patches of 500x500 pixels.

The NAFNet was given a much larger sample to learn from: 10 square patches 400 pixels to a side were used to train this instance, across just 16 epochs.

Both models were trained with mean squared error as the loss function, using the Adam optimizer, and evaluated with the mean average error metric.

\subsection{Results}
Sample predictions from each model on the validation task are presented in Table 1. The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.

\begin{figure}\label{fig4}
\includegraphics[width=\textwidth]{figures/sidebyside.png}
\caption{Validation images (left), with the images predicted by the ShabbyPages_NAFNet (center) and ShabbyPages_NAFNet_large (right) models.}
\end{figure} %[TODO: can we show this a better way?]

To compare the models' performance on the validation task, we considered the following metrics:
\begin{enumerate}
\item Root mean square error (RMSE)
\item Structural similarity index (SSIM)
\item Peak signal-to-noise ratio (PSNR)
\end{enumerate}

\begin{table}
\centering
\caption{Denoising performance on \emph{ShabbyReal} validation task}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Metric & Score \\
\hline
SSIM & \\
PSNR & \\
RMSE & \\
\hline
\end{tabular}
\end{table}

[TODO: add numbers and interpretation]
\section{Robustness Testing}
In this section, we examine the use of \emph{Augraphy} to add noise which challenges existing models.

One of \emph{Augraphy}'s \emph{raisons d'être} is denoising identity documents like driver's licenses, passports, and immigration forms; images of these documents are often generated in high-traffic environments like emergency rooms or border checkpoints, where the image capture hardware is frequently dirty or malfunctioning, producing noisy outputs.
Accurately capturing information is extremely important in these settings for human health and security, necessitating robust denoising and object detection models.

@@

\subsection{Face Detection Robustness Testing}
In this section, we use \emph{Augraphy} to investigate the robustness of object detection models on images that have been altered by \emph{Augraphy}.
Specifically, we explore using \emph{Augraphy} to add noise to images containing faces in order to test the robustness of face detection models.
In this way, we move beyond analyzing robustness of text-related tasks, but the images we analyze in this section can nonetheless appear in documents like newspapers \cite{newspaper-navigator} and identification documents \cite{midv-500}, which are often scanned from the physical world by noisy scanners.
Hence, it is important for image-focused models like image classifiers and object detection models to be robust to scanner-induced noise.

\begin{wraptable}{r}{5cm}
    \centering
    \caption{Face detection performance.}
    \begin{tabular}{lr}
    \toprule
        \textbf{Model} & \textbf{Accuracy} \\
        \midrule
        Azure & 57.1\%\\
        Google & 60.1\%  \\
        Amazon & 49.1\% \\
        UltraFace & 4.5\%\\
        \bottomrule
    \end{tabular}
    \label{tab:face-detection-results}
\end{wraptable}

@@

We described the process for using \emph{Augraphy} to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional U-Net and two NAFNet instances on this corpus.

>>>>

\title{Augraphy: A Data Augmentation Library for Document Images}
%\author{Alexander Groleau\inst{1,2} \and
%Kok Wei Chee\inst{1} \and
%Samay Maini\inst{1} \and
%Jonathan Boarman\inst{1}}
%
%\authorrunning{A. Groleau et al.}
%
%\institute{Sparkfish LLC (\email{augraphy@sparkfish.com})
%\and
%Left Associates LLC (\email{research@left.associates})}

@@

    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the original noise seen above, which is a real-life sample from RVL-CDIP. We re-created a clean reproduction and then created a noisy version by applying several \emph{Augraphy} augmentations.}

@@

\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce the level of complexity in the document lifecycle at seen in the real world.  Such real-world conditions and  features have direct implementations either within the library or on the development roadmap.

Some techniques exist for introducing these features into images of documents, including but not limited to the following:
\begin{enumerate}
\item Text can be generated independently of the paper texture, and can be overlaid onto the ``paper'' by a number of blending functions, allowing a variety of paper textures to be used.
\item Similarly, any markup features may be generated and overlaid by the same methods.
\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator's 3D mesh support here is excellent and has inspired \emph{Augraphy} to add similar functionality in its roadmap.  In the meantime, \emph{Augraphy} currently offers support for paper folds.
\end{enumerate}

@@

There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality:

@@

\section{Deep Learning with \emph{Augraphy}}
\emph{Augraphy} aims to facilitate rapid dataset creation, advancing the state of the art for document image analysis tasks.
This section describes a brief experiment in which \emph{Augraphy} was used to augment a new collection of clean documents, producing a new corpus which fills a feature gap in existing public datasets. This collection was used to train a denoising convolutional neural network capable of high-accuracy predictions, demonstrating \emph{Augraphy}'s utility for robust data augmentation.

@@

\subsection{Model Architecture}
To evaluate \emph{Augraphy}, we used an off-the-shelf Nonlinear Activation-Free Network (NAFNet), \cite{ref_nafnet}, making only minor alterations to the model's training hyperparameters, changing the batch size and learning epoch count to fit our training data.

\subsection{Data Generation}
Despite recent techniques (\cite{ref_tvt2040}, \cite{ref_vtssds}) for reducing the volume of input data required to train models, large datasets remain king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model to noise and increasing its capacity for generalization to new data.

@@

Another new dataset --- \emph{ShabbyReal} --- was produced as part of the larger \emph{ShabbyPages} corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper. \emph{ShabbyReal} is fully out-of-distribution for this experiment, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.

\subsection{Training Regime}
The NAFNet was given a large sample to learn from: for each image in the ShabbyPages set, we sampled ten patches of 400x400 pixels, using these to train the instance across just 16 epochs.

The model was trained with mean squared error as the loss function, using the Adam optimizer and cosine annealing learning rate scheduler, then evaluated with the mean average error metric.

\subsection{Results}
Sample predictions from the model on the validation task are presented in Figure \ref{fig:shabbyreal_denoised}. The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.

To compare the model's performance on the validation task, we considered the root mean square error (RMSE), structural similarity index (SSIM), and peak signal-to-noise ratio (PSNR) metrics.

\begin{table}
\centering
\caption{Denoising performance on \emph{ShabbyReal} validation task}\label{tab1}
\begin{tabular}{@{\hspace{2em}}l@{\qquad}@{\hspace{2em}}l@{\qquad}}
\toprule
\textbf{Metric} & \textbf{Score} \\
\midrule
SSIM & 0.71\\
PSNR & 32.52\\
RMSE & 6.52\\
\hline
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth]{figures/shabbyreal_denoised.png}
\caption{Sample \emph{ShabbyReal} noisy images (left) and their denoised counterparts (right).}
\label{fig:shabbyreal_denoised}
\end{figure}

As can be seen in Figure \ref{fig:shabbyreal_denoised}, the model was able to remove a significant amount of blur, line noise, shadowing from tire tracks, and watercoloring.

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth]{figures/shabbypages_denoising.png}
\caption{Sample \emph{ShabbyPages} noisy images (left), denoised by Shabby\_NAFNet (center), and groundtruth (right).}
\label{fig:shabbypages_denoising}
\end{figure}

\section{Robustness Testing}
In this section, we examine the use of \emph{Augraphy} to add noise which challenges existing models.

@@

\subsection{Face Detection Robustness Testing}
\begin{wraptable}{r}{6cm}
    \centering
    \caption{Face detection performance.}
    \begin{tabular}{lr}
    \toprule
        \textbf{Model} & \textbf{Accuracy} \\
        \midrule
        Azure & 57.1\%\\
        Google & 60.1\%  \\
        Amazon & 49.1\% \\
        UltraFace & 4.5\%\\
        \bottomrule
    \end{tabular}
    \label{tab:face-detection-results}
\end{wraptable}
In this section, we use \emph{Augraphy} to investigate the robustness of object detection models on images that have been altered by \emph{Augraphy}.
Specifically, we explore using \emph{Augraphy} to add noise to images containing faces in order to test the robustness of face detection models.
In this way, we move beyond analyzing robustness of text-related tasks, but the images we analyze in this section can nonetheless appear in documents like newspapers \cite{newspaper-navigator} and identification documents \cite{midv-500}, which are often scanned from the physical world by noisy scanners.
Hence, it is important for image-focused models like image classifiers and object detection models to be robust to scanner-induced noise.

@@

We described the process for using \emph{Augraphy} to create a new document image dataset containing synthetic real-world noise, then compared results obtained by training a convolutional NAFNet instance on this corpus.
